%Formatting Guidelines for Writing Dissertation.
\chapter*{Introduction}\label{intro}

After more than a century of development, thousands of homes have adopted cars, which have evolved from luxury goods to necessities in modern society since the world's first car was launched. The three pillars of energy efficiency, environmental preservation, and safety are the constant themes in the evolution of automotive technology. Pure electric vehicles, or new energy vehicles, have steadily gained industry attention due to their energy-saving and environmental benefits. Since, the turn of the twenty-first century, when oil prices began to rise and environmental pollution issues, such as "haze," became worse. %\cite{Real_Time_SOC_Estimation_Based_On_EKF_And_UKF_PTorin_Lei}.

At present, the world heading towards safe and green energy. One of the revolutionary research in energy saving and decreasing global warming is EVs. As the core component of energy-saving vehicles (EVs), the development of battery technology is the key to the industrialization of new energy vehicles. 

The promotion of pure electric vehicles has been hampered by people's worries about the range of electric cars, even though all major automakers are working to promote new energy models. Additionally, the frequent incidents of spontaneous combustion of electric cars in recent years have caused people to pay extra attention to the safety of electric cars. The safe and effective operation of the power battery in electric vehicles relies on a precise assessment of the battery status.

Among the EVs world, Lithium-ion batteries (LIB)  are uncrowned batteries, because of their energy density, reliability, and size constraints.  It is common knowledge that for safe use and enduring performance, a battery management system (BMS) is essential. However, what is less widely known is that during each discharge cycle, some unused energy remains in the battery. This is not due to technical design considerations, but to a phenomenon called cell-to-cell variation (C2CV). Due to physical characteristics, individual battery cells in a stack of multiple cells vary in capacity. In battery systems made from a series of connected cells, this leads to an imbalance in the state of charge (SoC) and SOH state of health during use. 
The battery state can be distinguished into two categories: those that can be directly measured, such as voltage, current, temperature, etc.; and those that cannot be directly measured[1] but can only be estimated using specific techniques, such as the battery's state of charge (SOC) and state of health (SOH).

This thesis mainly focuses on the SOC from the battery state diagram.

\input{Chap02/Introduction.tex}