\section*{Conclusion of Chapter \ref{ch:Architecture_Active_Balancing_BMS}}
Chapter \ref{ch:Architecture_Active_Balancing_BMS} is the core of this thesis, which describes the hardware setup for the wireless communication BMS. Since the hardware circuit of the BMS has a lot of subcircuits like auxiliary power supplies, charge pumps, ADC and communication circuits ...etc. I have limited my focus to explaining the main hardware blocks which address the active balancing BMS.

The main blocks involved in the active balancing of the batteries are buck-boost DC/DC converter, BLE, switch matrix, and controller. I have paid close attention to every circuit and the descriptions of the components. For active balancing in this project, I have limited my focus to particular hardware setup and topology (Type 2a pack to cell and vice versa). Still, I attempted to touch each topology flavor at least theoretically. Nonetheless, we can follow any of the active balancing topologies which I have described in chapter 2. Picking the active balancing topology is completely an independent choice for the user based on the application. This chapter took quite a long trip across different hardware and working principles of each circuit .... overall the trip went very successfully because it summarized all the hardware concepts of the active balancing for the batteries.

Active balancing can be expensive for low-level battery applications, but it can save a  lot of energy if we consider large applications like EVs.