\chapter{Battery Modeling and Emulation}\label{ch:Battery_Modeling_Emulation}
The \textit{Battery} is a complex composition of lethal chemicals that are very hard to handle in terms of safety and maintenance. So, is those petroleum vehicles safe? No, Not at all petroleum products and vehicles are much more dangerous not only in terms of environmental pollution it in terms of safety and measures. Then we should raise the question of what stopping modern engineers to transition from petroleum engines to Battery vehicles. And which wall stopping us from battery usage? Well, to answer all the above questions we need to look back at the evolution of vehicles, the petroleum vehicle fetus came to this world nearly a century ago. Engineers thoroughly studied and learned how to handle petroleum products and petroleum vehicles. Undoubtedly, EVs are the gift of modern technology, but it is essential to study institutionally the battery characteristics and the testing.

It is the prime responsibility of every Electrical engineer who works in EVs/Battery systems to ensure the safety of mankind. Considering all the facts, I have decided to make safety and sophisticated system for engineers to test the BMS and play with BMS without interacting with the physical batteries. The \textit{Part I} of Chapter \ref{ch:Battery_Modeling_Emulation} gives more elaboration about the battery modeling and battery constructional theory. \textit{Part II} facilitates understanding of Battery model implementation and BMS simulation through coding.

\input{Chap06/Chap06_BatteryModeling}
\input{Chap06/Chap06_Emulation}
\input{Chap06/Chap06_BatteryModeling_Results}

\section{Summery of Chapter \ref{ch:Battery_Modeling_Emulation}}
Part I of the chapter \ref{ch:Battery_Modeling_Emulation} described the mathematical modeling of the battery with One-time and two-time constant equivalent circuit components. An extended subsection of Part I helped to estimate the OTC and TTC model parameters with the SOC curve which became the fundamental base for the battery pack power analyzer design. Part I also briefed about the discrete-time implementation of the OTC and TTC model for the battery. The discrete-time OTC and TTC model equations are useful for estimating the battery soc with advanced algorithms like Kalman, extended Kalman, and Columb-Extended Kalman. The most satisfactory conclusion in Part I can be seen in Part II, implementing battery models with the script and emulating with lab instruments. Nonetheless, for a more analytical and mathematical understanding of batteries, I diverted read attention toward the reference papers mentioned in the Bibliography. Part II talks about the practical implementation of Part I in terms of script and different instruments. Starting subsection of Part II walks through several instruments' specifications and configurations used in this project. This chapter is indeed a bit lengthy and diversified. Because battery modeling and implementation got to go together which is the reason I took extra liberty to extend this chapter more descriptive.
I got less opportunity to describe the script but I have pushed everything to GitHub and referenced the links in miscellaneous.

To sum up the results came out from this chapter are convincing, and this can be still pursued further to develop a sophisticated graphical interface for the application. In the battery modeling, I have used the Columb counting approach for estimating the battery SOC, this can be still dragged into higher algorithms and can also increase the robustness of the model by adding more and more battery time constant models.