\thispagestyle{empty} 
\SpecialTitle{Acknowledgment}

\noindent First and foremost, I express my deep appreciation and gratitude to my advisor,
\textit{Prof. Piero Malcovati} for his active support and crucial guidance throughout my master's Thesis program. It’s his guidance that provided me with the perspective and intuitive skills along with analytical capabilities that helped me to improve my technical
understanding. His constructive approach and passion for his job are very inspirational to us. His positive words and encouragement always cheered me up, to gain productivity and proactiveness.

I also like to extend my gratitude to acknowledge my co-advisor and Manager of Application Team in \textit{Inventvm}, \textit{Eng. Domenico Granozio} for his association and active collaboration from Inventvm. The challenging tasks assigned to me enhance and outreach my potential. His supervision and
suggestions always helped me to set and organize the agenda, follow it systematically, and accomplish the tasks within the specified time.


Further, I would like to thank \textit{INVENTVM} Pavia for providing me with the resources and the opportunity to execute my Thesis idea. During the Master Thesis while I spent 11 months in the Inventvm, \textit{Luigi Pinna} was always there to help me out, in terms of instrument setup and lab activity challenges, so I also thank him for his great contribution.

A Significant contribution from my colleagues in the Inventvm application team must be acknowledged at this moment each, and everyone has been part of my one year, and they made me the happiest person in the work environment. Every colleague in the inventvm application team made my work more productive with healthy discussions and performances. \textit{Riccardo, Flavio}, and \textit{Antonino} were there to have a conversation full of amusement.

Last but not least, I would like to thank my beloved parents, who fostered me by teaching me the value of education, for their unconditional love and support towards me, for encouraging me in every crucial step of my life and believing in me. Thanks to my gorgeous sister \textit{Ashwini} who gives me a feeling of myself being her pride, for her immense support.

\begin{flushright}
    Harish Kumar Shivaramappa\\
    \textit{University of Pavia}\\
    December 2022
\end{flushright}


