\chapter*{Introduction}
After more than a century of development, thousands of homes have adopted cars, which have evolved from luxury goods to necessities in modern society since the world's first car was launched. The three pillars of energy efficiency, environmental preservation, and safety are the constant themes in the evolution of automotive technology. Pure electric vehicles, or new energy vehicles, have steadily gained industry attention due to their energy-saving and environmental benefits. Since, the turn of the twenty-first century, when oil prices began to rise and environmental pollution issues, such as "haze," became worse \cite{Real_Time_SOC_Estimation_Based_On_EKF_And_UKF_PTorin_Lei}.

At present, the world heading towards safe and green energy. One of the revolutionary research in energy saving and decreasing global warming is EVs. As the core component of energy-saving vehicles (EVs), the development of battery technology is the key to the industrialization of new energy vehicles. 

The promotion of pure electric vehicles has been hampered by people's worries about the range of electric cars, even though all major automakers are working to promote new energy models. Additionally, the frequent incidents of spontaneous combustion of electric cars in recent years have caused people to pay extra attention to the safety of electric cars. The safe and effective operation of the power battery in electric vehicles relies on a precise assessment of the battery status.

Two categories of battery state can be distinguished: those that can be directly measured, such as voltage, current, temperature, etc.; and those that cannot be directly measured[1] but can only be estimated using specific techniques, such as the battery's state of charge (SOC) and state of health (SOH).

The practical application and simple hardware touch have received more emphasis in my thesis. The project is cross-disciplinary and incorporates the use of software, hardware, modeling using mathematics, and analytics. I'm keeping five objectives for my thesis, which is the project's topic because the project is much larger and more standardized.
The five modules in this report are the areas that I've illustrated.
The purpose and format of my thesis are described in the parts that follow.

\section*{Wireless Architecture for BMS}
The biggest problem in today's EV technology is maintaining the weight limit to save energy, in conventional EVs the weight of the wires used for sensing the matter and sense is huge.  Reducing all those wire weights could be a magical moment for EVs. One of the objectives of this project set up safe and sophisticated wireless communication BMS. I have attempted to describe the wireless architecture for the BMS and BLE modules design in chapter 1. I have also tried to explain the general considerations for RF layout design and placements. 
