\chapter{Preface}
When started my Microelectronics master's program at the University of Pavia, I was wondering about the future of microelectronics in the domain of electric vehicle and sustainable energy management because I have witnessed personally how world leaders are crumbling to fix global warming and climate change. The idea of making global warming free through sustainable energy drove me to explore electrical vehicles and power management. As I was intensively researching my self about electrical vehicles and battery management systems, I got an opportunity to enroll LM+ program at the university of Pavia which is doing an internship through the university in corporate companies for one year.\\
\indent Among the LM+ opportunities, I have noticed that Inventvm a dynamic young Italian company is doing research on Battery management systems for electrical vehicles. Since my interest is to work in power management and sustainable energy management, the Inventvm BMS project became a cherry on the pie for me. During the process, I met Eng. Domenico (Inventvm project BMS project manager), his idea of an elaboration made me more curious about the project and I stretched my legs immediately to the Inventvm on Feb 2020.\\
\indent As I was stepping into Inventvm I started to experience the radiation of the knowledge from the engineers because they are not kids like me. As a young rookie in technology, I start to learn more about the hardware and software of the project because the bus(project) is already started way before I join to the company. That was ok! because at the age of 10 I smoked the LED placing it in 230V mains, what ??????? YES that's right, for sure the led did not glow bright, but my brain became to dig into why LED got burned despite the black smoke on the face while LED burned. Anyway, later I was educated by my father(of course he is an electrician) that LED needs some kind of electronic circuit to make it glow. when my father made LED glow, That was WoW, "astonishing"! LED was not too much bright enough though. This idea of making education by failure became fascinating this same strategy worked for me to understand this in the industry too quickly not to miss the bus. There are always my colleagues who gave me a shoulder to shoulder when I was stuck in some technological part.\\
\indent Before my Master's, I worked with Analog Device Inc as IoT application Engineer and System Testing Engineer for Highpower circuits In NEXTGEN computers helped in my current project to understand the Wireless communication environment and power management. My experience in these two prime companies laid the foundation for analytical skills and problem-picking skills throughout the project. Nevertheless, the key motivation was my father and all my teachers who educated me throughout my life to contribute well to nature and humanity. Nonetheless, Prof malcovati has been a gem among all my honorable teacher's treasury who shined bright in my way. Thanks......!